Forecasting interrupted time series

### 2024-05-17 response_letter/response_letter_JORS.qmd

---
title: "Response letter - Manuscript ID 249381018"
format:
  pdf:
    pdf-engine: pdflatex
    papersize: a4
    geometry: "margin = 2.2cm"
    header-includes:
      - \usepackage{bm,mathpazo}
      - \usepackage[lf]{FiraSans}
      - \usepackage[scale=0.9]{sourcecodepro}

---

@@

_Comment 2: I like that the authors contrast the topic with others that it may be confused with. But need to check the claim that it is indeed the first to address this problem._

**Response:** Thank you for your comment. The idea for this paper emerged from our close contact with practitioners, who highlighted the challenges they face in forecasting time series data affected by COVID-19, particularly in handling observations impacted by the disruption. Following these discussions, we carried out a search to find out if any existing papers addressed this issue, but we could not find any published research in this area. To our knowledge, this is the first study to describe and compare general strategies for forecasting interrupted time series, such as COVID-19-affected data.

_Comment 3: The paper is well written, but in terms of contributions, it falls short of the expectations for an original research paper. Improvement avenues are proposing a viable new method that has advantages over these existing methods, or a large-scale empirical research with carefully curated set of actual data representing different interruption patterns from different domains._

**Response**: Thank you for your feedback. We appreciate your comments on the writing quality and your recommendations for improving the paper's contributions. We believe that the originality of our research comes from addressing the actual challenges that many forecasters and modellers experience when their time series data is disturbed by recommending multiple viable and reliable strategies suitable for different cases. We recognise that presenting a new technique may be an exciting direction, but it is not the aim of this paper. So we have included it as a potential topic for future research in this area. Also, we included two empirical datasets from two different application areas in the paper. Moreover, the whole paper is reproducible, and the datasets and R codes are accessible on GitHub, allowing strategies to be tailored to any dataset in any application.

We have added the following paragraph in the revised manuscript.

@@

In future work, a large scale empirical study covering several types of disruption could be conducted to provide deeper insights and any possible link between strategies and types of disruption events. We have included the following paragraph in the conclusion section of the revised manuscript:

\textcolor{teal}{This study proposes multiple viable strategies for forecasting time series data interrupted by different type of events. Future research could focus on exploring new strategies for handling such disrupted time series, or enhancing probabilistic forecasting methods that are designed specifically for such data. Large-scale empirical research on further exploring which strategy may work best in different scenarios also provide useful insights.}

_Comment 3. The authors provide some visualizations on the forecasting. This should be appreciated since it is quite straightforward. However, the authors may not expect the readers to judge the optimal strategy from these figures. Instead, the authors should consider some out-of-sample validation and may introduce some metrics or measures to evaluate the performance different strategies._

**Response**: The visualizations are intended to help the reader understand the effect and intent of different strategies. In determining which strategy to apply in each case, it is important to think through what is being assumed, and what data are being used. We think the visualizations help the reader do that. Also, it does not always make sense to do a quantitative comparison of forecast accuracy. We have attempted to address this issue by adding the following paragraph in the discussion section.

@@

**Response:** Thank you for this comment. We do not believe the addition of descriptive statistics will add anything useful to the manuscript. We argue that the usefulness of descriptive statistics for time series analysis is limited. First, they cannot highlight patterns in the data, identify unusual observations, describe changes over time, or help to understand relationships between variables. Second, they could be misleading, since similar statistics can stem from very different datasets (please see Anscombe’s Quartet).

We have provided the raw data, and we have provided time plots to help visualize the data. Each data set is described in Section 3.

_Comment 5. Literature must reflect the relevant studies i.e._

  a) _OntoCOVID: Ontology for Semantic Modeling of COVID19 Statistical Data Authors Shaukat Ali, Shah Khusro, Sajid Anwar, Abrar Ullah Publication date 2022 Book Proceedings of International Conference on Information Technology and Applications Pages 83-194 Publisher Springer, Singapore_
  b) _COVID-19 patient count prediction using LSTM M Iqbal, F Al-Obeidat, F Maqbool, S Razzaq, S Anwar, A Tubaishat, ... IEEE Transactions on Computational Social Systems 8 (4), 974-981_
  c) _Countering malicious URLs in internet of things using a knowledge-based approach and a simulated expert S Anwar, F Al-Obeidat, A Tubaishat, S Din, A Ahmad, FA Khan, G Jeon, ... IEEE Internet of Things Journal 7 (5), 4497-4504_

### 2024-05-17 fits.qmd
Added authors to first page

---
title: "Forecasting interrupted time series"
author:
- name: Rob J Hyndman
  affiliations:
    - department: Department of Econometrics & Business Statistics
    - name: Monash University
    - city: Clayton VIC
    - country: Australia
    - postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Bahman Rostami-Tabar
  affiliations:
    - name: Cardiff Business School
    - postal-code: Wales CF10 3EU
    - country: United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
abstract: "Forecasting interrupted time series data is a major challenge for forecasting teams, especially in light of events such as the COVID-19 pandemic. This paper investigates several strategies for dealing with interruptions in time series forecasting, including highly adaptable models, intervention models, marking interrupted periods as missing, forecasting what may have been, downweighting the interruption period, and ensemble models.  Each approach offers specific advantages and disadvantages, such as adaptability, memory retention, data integrity, flexibility, and accuracy. We evaluate the effectiveness of these strategies using two actual datasets that were interrupted by COVID-19, and we provide recommendations for how to handle these interruptions. This work contributes to the literature on time series forecasting, offering insights for academics and practitioners dealing with interrupted data in numerous domains."
keywords:
  - counterfactual forecasting
  - COVID-19
  - disruptive events
  - intervention analysis
  - structural breaks
bibliography: references.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: true
cover: false
linestretch: 1.5
format:
  wp-pdf:
    include-in-header: header.tex
    keep-tex: true
---

>>>>

---
title: "Forecasting interrupted time series"
author:
- name: Rob J Hyndman
  affiliations:
    - department: Department of Econometrics & Business Statistics
    - name: Monash University
    - city: Clayton VIC
    - country: Australia
    - postal-code: 3800
  email: Rob.Hyndman@monash.edu
- name: Bahman Rostami-Tabar
  affiliations:
    - name: Cardiff Business School
    - postal-code: Wales CF10 3EU
    - country: United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
  corresponding: true
abstract: "Forecasting interrupted time series data is a major challenge for forecasting teams, especially in light of events such as the COVID-19 pandemic. This paper investigates several strategies for dealing with interruptions in time series forecasting, including highly adaptable models, intervention models, marking interrupted periods as missing, forecasting what may have been, downweighting the interruption period, and ensemble models.  Each approach offers specific advantages and disadvantages, such as adaptability, memory retention, data integrity, flexibility, and accuracy. We evaluate the effectiveness of these strategies using two actual datasets that were interrupted by COVID-19, and we provide recommendations for how to handle these interruptions. This work contributes to the literature on time series forecasting, offering insights for academics and practitioners dealing with interrupted data in numerous domains."
keywords:
  - counterfactual forecasting
  - COVID-19
  - disruptive events
  - intervention analysis
  - structural breaks
bibliography: references.bib
wpnumber: no/yr
jelcodes: ""
blind: false
cover: false
linestretch: 1.5
format:
  wp-pdf:
    include-in-header: header.tex
    keep-tex: true
---
